Ethereum: Un Registro Generico delle Transazioni Sicuro e Decentralizzato \\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-02-01 Paper.tex
Update Paper.tex

Niente altro che \textbf{extraData} debba contenere almeno 32 byte.

@@

Con il fine di evitare problemi relativi all'abuso del network e per aggirare le inevitabili derivanti della completezza di Turing, tutta la computazione programmabile in Ethereum è soggetta alla fee. The fee schedule is specified in units of \textit{gas} (see Appendix \ref{app:fees} for the fees associated with various computation). Thus any given fragment of programmable computation (this includes creating contracts, making message calls, utilising and accessing account storage and executing operations on the virtual machine) has a universally agreed cost in terms of gas.

Every transaction has a specific amount of gas associated with it: \textbf{gasLimit}. This is the amount of gas which is implicitly purchased from the sender's account balance. The purchase happens at the according \textbf{gasPrice}, also specified in the transaction. The transaction is considered invalid if the account balance cannot support such a purchase. It is named \textbf{gasLimit} since any unused gas at the end of the transaction is refunded (at the same rate of purchase) to the sender's account. Gas does not exist outside of the execution of a transaction. Thus for accounts with trusted code associated, a relatively high gas limit may be set and left alone.

In general, Ether used to purchase gas that is not refunded is delivered to the \textit{beneficiary} address, the address of an account typically under the control of the miner. Transactors are free to specify any \textbf{gasPrice} that they wish, however miners are free to ignore transactions as they choose. A higher gas price on a transaction will therefore cost the sender more in terms of Ether and deliver a greater value to the miner and thus will more likely be selected for inclusion by more miners. Miners, in general, will choose to advertise the minimum gas price for which they will execute transactions and transactors will be free to canvas these prices in determining what gas price to offer. Since there will be a (weighted) distribution of minimum acceptable gas prices, transactors will necessarily have a trade-off to make between lowering the gas price and maximising the chance that their transaction will be mined in a timely manner.

>>>>

E' sufficiente che \textbf{extraData} contenga almeno 32 byte.

@@

Con il fine di evitare problemi relativi all'abuso del network e per aggirare le inevitabili derivanti della completezza di Turing, tutta la computazione programmabile in Ethereum è soggetta alla fee. Il tariffario è specificato in unità di \textit{gas} (see Appendix \ref{app:fees} per le fee associate con le diverse computazioni. Perciò ogni dato frammento di computazione programmabile (questo include la creazione di contratti, fare messaggi di chiamata, utilizzando ed accedendoo all'account di storage ed eseguendo operazioni sulla macchina virtuale) ha un costo universalmente accettato in termi di gas.

Ogni transazione ha uno specifico ammontare di gas con cui è associata: \textbf{gasLimit}. Questo è l'ammontare del gas che è acquistato implicitamente attraverso il saldo dell'account del mittente. L'acquisto avviene al pattuito \textbf{gasPrice}, anche specificato nella transazione. La transazione è considerata invalida se il saldo dell'account non può sostenere il suddetto acquisto. Prende il nome di \textbf{gasLimit} poichè ogni gas inutilizzato alla fine della transazione è restituito (allo stesso prezzo dell'acquisto) all'account del mittente. Il Gas non esiste al di guori dell'esecuzione di una transazione. Quindi per gli account con un codice associato di cui si ha fiducia, può essere impostato un limite di gas relativalemnte alto senza la necessità di modificarlo.

In generale, l'Ether impiegato per acquistare il gas che non è rimborsabile è consegnato al \textit{beneficiary} indirizzo, the address of an account typically under the control of the miner. Transactors are free to specify any \textbf{gasPrice} that they wish, however miners are free to ignore transactions as they choose. A higher gas price on a transaction will therefore cost the sender more in terms of Ether and deliver a greater value to the miner and thus will more likely be selected for inclusion by more miners. Miners, in general, will choose to advertise the minimum gas price for which they will execute transactions and transactors will be free to canvas these prices in determining what gas price to offer. Since there will be a (weighted) distribution of minimum acceptable gas prices, transactors will necessarily have a trade-off to make between lowering the gas price and maximising the chance that their transaction will be mined in a timely manner.
